### 2022-04-27 README.Rmd
some to show enmac4
baseline and enmac4 without jittering
add libraries in 0

```{r echo=FALSE, message=FALSE, warning=FALSE}
planned_network = sf::st_read("https://github.com/U-Shift/biclar/releases/download/0.0.1/CyclingPlans2021.gpkg", quiet = TRUE)

@@

>>>>

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
planned_network = sf::st_read("https://github.com/U-Shift/biclar/releases/download/0.0.1/CyclingPlans2021.gpkg", quiet = TRUE)

@@

```{r echo=FALSE}
knitr::include_graphics("man/figures/existingplanned.png")
```

We can view it in an [interactive map here](https://ushift.tecnico.ulisboa.pt/content/tml/RedeExistentePrevista.html).
